Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Fix reference to adjacency and index

\begin{defn}{(Adjacent)}
  A subscript $S$ is said to be \emph{adjacent at index $j$} of another
  subscript $S'$ if for every index $i$ except $j$, $\pi_i(S) = \pi_i(S')$ but
  at $j$ then $\pi_j(S) \neq \pi_i(S')$ such that $|S| = |S'| + 1$.

\todo{%
  Not sure how to rewrite the following as I have a bit of hard time parsing it.
}

  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique adjacent at index $i$ of a subscript, if it exists, is given by the
  following partial function:
%
  \begin{align*}
    \mathit{adjacent}(S,i) & = \prod^{N}_{j=1} \mathit{shift}(S,i,j) &
%
    \mathit{shift}(S,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(S) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(S) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(S)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Hm- I guess uniqueness follows from this being a function rather
  than a relation? Seems fine no problem to prove- }
\end{proof}

\todo{On the following, add some intutition first- what is this and
  what is it for?}
\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{align*}
    \mathit{ES}_{P,0} & = \{ p \in P \mid \forall \i.\ \pi_i(p) \in \interv{-1}{1}{} \} \\
    \mathit{ES}_{P,d} & =
      \{ p \in P \mid \forall i.\
      p_i \notin [-1,1] \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{close\_neighbour}(p,i) \}
  \end{align*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then
  $\bigcup_{1 \leq d \leq D} \mathit{ES}_{P,d}$, where $D$ is the maximum origin
  distance in $P$.
\end{defn}

>>>>

\begin{defn}{(Adjacent)}
  A subscript $S$ is said to be \emph{adjacent at index $j$} of another
  subscript $S'$ if for every index $i$ except $j$, $\pi_i(S) = \pi_i(S')$ but
  at $j$ then $\pi_j(S) \neq \pi_j(S')$ such that $|S| = |S'| + 1$.
\end{defn}
%
\begin{prop}
  The unique adjacent at index $i$ of a subscript, if it exists, is given by the
  following partial function:
%
  \begin{align*}
    \mathit{adjacent}(S,i) & = \prod^{N}_{j=1} \mathit{shift}(S,i,j) &
%
    \mathit{shift}(S,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(S) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(S) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(S)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\todo{Hm- I guess uniqueness follows from this being a function rather
  than a relation? Seems fine no problem to prove- }
\end{proof}

\todo{On the following, add some intutition first- what is this and
  what is it for?}
\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{align*}
    \mathit{ES}_{P,0} & = \{ p \in P \mid \forall \i.\ \pi_i(p) \in \interv{-1}{1}{} \} \\
    \mathit{ES}_{P,d} & =
      \{ p \in P \mid \forall i.\
      p_i \notin [-1,1] \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{adjacent}(p,i) \}
  \end{align*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then
  $\bigcup_{1 \leq d \leq D} \mathit{ES}_{P,d}$, where $D$ is the maximum origin
  distance in $P$.
\end{defn}
